Modeling the Circumnuclear Mediums and Accetion Rates of Quiescent Supermassive Black Holes

### 2015-01-13 ms.tex
Changing some of the comments in the solution table.

\begin{table*}
\centering
\begin{minipage}{18cm}
\caption{}
\begin{tabular}{lccccccccccccc}
\hline
{$M_{\bullet,8}$} & {$v_{w}$} & {$\gamma$} & {$r_b$} & {$\dot{M}/\dot{M}_{\rm Edd}$} & {$t_{\rm cool}/t_{\rm ff} (r_s)$} & {comments}\\
\hline
0.01 & 300.0 & 0.8 & 100.0 & $ 3.2 \times 10^{ -4 }$ & 4.7 & rb in fact
unresolved \\
0.01 & 600.0 & 0.8 & 100.0 & $ 5.5 \times 10^{ -5 }$ & $ 3.2 \times
10^{ 2 }$ &  rb in fact unresolved\\
0.01 & 1200.0 & 0.8 & 100.0 & $ 9.4 \times 10^{ -6 }$ & $ 1.5 \times
10^{ 4 }$ &  rb in fact unresolved\\
0.1 & 300.0 & 0.8 & 100.0 & $ 2.5 \times 10^{ -3 }$ & 0.29 & energy
cons on outer grid \\
0.1 & 600.0 & 0.8 & 100.0 & $ 1.8 \times 10^{ -4 }$ & 97 &  \\
0.1 & 1200.0 & 0.8 & 100.0 & $ 3.1 \times 10^{ -5 }$ & $ 4.8 \times
10^{ 3 }$ &  energy cons on inner grid\\
1 & 300.0 & 0.8 & 100.0 & $ 1.6 \times 10^{ -2 }$ & $ 5.6 \times 10^{ -2 }$ &  \\
1 & 600.0 & 0.8 & 100.0 & $ 7.3 \times 10^{ -4 }$ & 21 &  \\
1 & 1200.0 & 0.8 & 100.0 & $ 9.9 \times 10^{ -5 }$ & $ 1.5 \times 10^{ 3 }$ &  \\
0.1 & 300.0 & 0.8 & 50.0 & $ 2.0 \times 10^{ -3 }$ & 0.46 &  \\
0.1 & 300.0 & 0.8 & 300.0 & $ 7.2 \times 10^{ -3 }$ & $ 6.7 \times 10^{ -2 }$ &  \\
0.1 & 300.0 & 0.8 & 200.0 & $ 5.3 \times 10^{ -3 }$ & 0.12 &  \\
0.1 & 300.0 & 0.8 & 400.0 & $ 8.9 \times 10^{ -3 }$ & $ 4.7 \times 10^{ -2 }$ &  \\
1 & 300.0 & 0.8 & 50.0 & $ 8.2 \times 10^{ -3 }$ & 0.19 &  \\
1 & 300.0 & 0.8 & 200.0 & $ 3.6 \times 10^{ -2 }$ & $ 1.7 \times 10^{
  -2 }$ &  possible issue w/ conv \\
1 & 300.0 & 0.8 & 300.0 & $ 5.2 \times 10^{ -2 }$ & $ 9.8 \times 10^{
  -3 }$ &  possible issue w/ conv ; rb=400 pc was unsuccessful\\
\hline
\label{table:models}
\end{tabular}
\end{minipage}
\end{table*}

>>>>

\begin{table*}
\centering
\begin{minipage}{18cm}
\caption{}
\begin{tabular}{lccccccccccccc}
\hline
{$M_{\bullet,8}$} & {$v_{w}$} & {$\gamma$} & {$r_b$} & {$\dot{M}/\dot{M}_{\rm Edd}$} & {$t_{\rm cool}/t_{\rm ff} (r_s)$} & {comments}\\
\hline
0.01 & 300.0 & 0.8 & 100.0 & $ 3.2 \times 10^{ -4 }$ & 4.7 & rb in fact
unresolved \\
0.01 & 600.0 & 0.8 & 100.0 & $ 5.5 \times 10^{ -5 }$ & $ 3.2 \times
10^{ 2 }$ &  rb in fact unresolved\\
0.01 & 1200.0 & 0.8 & 100.0 & $ 9.4 \times 10^{ -6 }$ & $ 1.5 \times
10^{ 4 }$ &  rb in fact unresolved\\
0.1 & 300.0 & 0.8 & 100.0 & $ 2.5 \times 10^{ -3 }$ & 0.29 & energy
cons on outer grid \\
0.1 & 600.0 & 0.8 & 100.0 & $ 1.8 \times 10^{ -4 }$ & 97 &  \\
0.1 & 1200.0 & 0.8 & 100.0 & $ 3.1 \times 10^{ -5 }$ & $ 4.8 \times
10^{ 3 }$ &  energy cons on inner grid\\
1 & 300.0 & 0.8 & 100.0 & $ 1.6 \times 10^{ -2 }$ & $ 5.6 \times 10^{
  -2 }$ &  TI\\
1 & 600.0 & 0.8 & 100.0 & $ 7.3 \times 10^{ -4 }$ & 21 &  \\
1 & 1200.0 & 0.8 & 100.0 & $ 9.9 \times 10^{ -5 }$ & $ 1.5 \times 10^{
  3 }$ &  \\
1 & 300.0 & 0.8 & 50.0 & $ 8.2 \times 10^{ -3 }$ & 0.19 &  \\
1 & 300.0 & 0.8 & 200.0 & $ 3.6 \times 10^{ -2 }$ & $ 1.7 \times 10^{
  -2 }$ &  TI/convergence \\
1 & 300.0 & 0.8 & 300.0 & $ 5.2 \times 10^{ -2 }$ & $ 9.8 \times 10^{
  -3 }$ &  TI/convergence\\
1 & 300.0 & 0.8 & 300.0 & $ 5.2 \times 10^{ -2 }$ & $ 9.8 \times 10^{
  -3 }$ &  TI/run unsuccessful\\
0.1 & 300.0 & 0.8 & 50.0 & $ 2.0 \times 10^{ -3 }$ & 0.46 &  \\
0.1 & 300.0 & 0.8 & 300.0 & $ 7.2 \times 10^{ -3 }$ & $ 6.7 \times 10^{ -2 }$ &  \\
0.1 & 300.0 & 0.8 & 200.0 & $ 5.3 \times 10^{ -3 }$ & 0.12 &  \\
0.1 & 300.0 & 0.8 & 400.0 & $ 8.9 \times 10^{ -3 }$ & $ 4.7 \times 10^{ -2 }$ &  \\

\hline
\label{table:models}
\end{tabular}
\end{minipage}
\end{table*}
